### 2010-02-26 trunk/deliverables/D2_2_Ontology/properties.tex
the final version that will be submitted to the EC. Mainly revised ontology code, introduction and conclusion
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@603 d8b0c59b-6544-0410-94d9-83a5658a058e

\textcolor{white}{\textbf{description}} & Many kinds of components in FAST can contain other components: 
screenflows contain screens, screens contain forms or form elements, etc.
It points to a resource reference to give a unique `id' to each component
within the resource. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property indicates which actions are associated and can be perfomed within 
a screen component. \\ \hline

@@

\textcolor{white}{\textbf{description}} & URL of the executable code of a particular building block (currently screens or screen components). \\ \hline

@@

\textcolor{white}{\textbf{description}} & Links the template of a resource as used in the palette or catalogue of available resources to its copy, as used in a particular screen flow. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property is the language the library is written in. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property indicates which libraries are used by a screen component. \\ \hline

@@

\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Fact}}{subs:Fact} \\ \hline
\textcolor{white}{\textbf{range}} & \texttt{xsd:Condition} \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property links certain type of resources to its post-condition, 
i.e., the facts that are produced once the screen or screenflow has been 
executed. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property links certain type of resources to its pre-condition, i.e., 
the facts that need to be fulfilled in order for this screen or screenflow to be 
reachable. \\ \hline

@@

\textcolor{white}{\textbf{description}} & An image which shows a particular screen or screenflow in action, to 
aid users in deciding which screen or screenflow to choose out of many. \\ \hline

@@

\textcolor{white}{\textbf{description}} & Links the copy of a resource as used in a particular screen flow to its template, as used in the palette or catalogue of available resources. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property links a buildiong block to a Trigger. \\ \hline

@@

\textcolor{white}{\textbf{description}} & Facts can be set to a specific scope: design time, execution time,
or both of them. This property will define when they have to be taken into account by the
inference engine or reasoner. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property indicates concepts used within a building block, without being a 
pre- or post-condition. \\ \hline

>>>>

\textcolor{white}{\textbf{description}} & Many kinds of components in FAST can contain other components: screenflows contain screens, screens contain forms, operators and resources, forms contain form elements, etc. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property indicates which actions are associated and can be perfomed within a screen component. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property links to the executable code of a particular building block (currently screens or screen components). \\ \hline

@@

\textcolor{white}{\textbf{description}} & Links the template of a building block as used in the palette or catalogue of available building blocks to its copy, as used in a particular screen flow. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property defines the programming language a particular programming library uses. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property indicates which programming libraries are used by the code of a screen component. \\ \hline

@@

\textcolor{white}{\textbf{range}} & \texttt{xsd:String} \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property links certain type of building blocks to their post-condition, i.e., the facts that are produced once the building block has been executed. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property links certain type of building blocks to their pre-condition, i.e., the facts that need to be fulfilled in order for the building block to be reachable. \\ \hline

@@

\textcolor{white}{\textbf{description}} & An image which shows a particular screen or screenflow in action, to aid users in deciding which screen or screenflow to choose out of many. \\ \hline

@@

\textcolor{white}{\textbf{description}} & Links the copy of a building block as used in a particular screen flow to its template, as used in the palette or catalogue of available building blocks. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property links a buildiong block to a trigger. \\ \hline

@@

\textcolor{white}{\textbf{description}} & Facts can be set to a specific scope: design time, execution time, or both of them. This property defines how they have to be taken into account by the inference engine or reasoner. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property indicates concepts used within a building block, without being a pre- or post-condition. \\ \hline
